# Data Analyst Test


```{r, include=FALSE}
tutorial::go_interactive()
```

# Statistical thinking and programming (60%)

### Question 1 {-}

You are given the dataset called `insurance_dataset.csv` contains 1338 observations (rows) and 7 features (columns). The insurance data contains 4 numerical features (age, bmi, children, expenses) and 3 nominal features (sex, smoker and region). We are interested in which determinants are significant for predicting the insurance expenses.

```{r ex="play_around", type="pre-exercise-code"}
insurance_dataset <- read.csv('insurance_dataset.csv', header = T)
```

```{r ex="play_around", type="sample-code", tut = TRUE}



# Print out a

```

## Critical thinking (30%)

```{r ex="create_a", type="pre-exercise-code"}
b <- 5
```

```{r ex="create_a", type="sample-code"}
# Create a variable a, equal to 5


# Print out a

```

```{r ex="create_a", type="solution"}
# Create a variable a, equal to 5
a <- 5

# Print out a
a
```

```{r ex="create_a", type="sct"}
ex () %>% check_object("a")
test_output_contains("a", incorrect_msg = "Make sure to print `a`.")
success_msg("Great!")
```


## Visualization (10%)

All chapter sections start with a second-level (`##`) or higher heading followed by your section title, like the sections above and below here. You can have as many as you want within a chapter.

### An unnumbered section {-}

Chapters and sections are numbered by default. To un-number a heading, add a `{.unnumbered}` or the shorter `{-}` at the end of the heading, like in this section.
