```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')

tutorial::go_interactive(greedy=FALSE)
```

# Data Analyst Test

<script src=https://cdn.datacamp.com/datacamp-light-latest.min.js></script>

## Statistical thinking and programming (60%)

### Question 1 {-}

You are given the dataset called `insurance_dataset.csv` contains 1338 observations (rows) and 7 features (columns). The insurance data contains 4 numerical features (age, bmi, children, expenses) and 3 nominal features (sex, smoker and region). We are interested in which determinants are significant for predicting the insurance expenses.

```{r ex="play_around", type="pre-exercise-code", tut = TRUE}
insurance_dataset <- read.csv('insurance_dataset.csv', header = T)
```

```{r ex="play_around", type="sample-code", tut = TRUE}
# Create a variable a, equal to 5


# Print out a

```

## Critical thinking (30%)

## Visualization (10%)

All chapter sections start with a second-level (`##`) or higher heading followed by your section title, like the sections above and below here. You can have as many as you want within a chapter.

### An unnumbered section {-}

Chapters and sections are numbered by default. To un-number a heading, add a `{.unnumbered}` or the shorter `{-}` at the end of the heading, like in this section.
